\documentclass[a4paper]{article}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=cyan,
    urlcolor=cyan
}
\usepackage{url}
\usepackage[authoryear]{natbib}


\begin{document}

    \begin{flushright}
        {\huge{Christopher Gandrud, Ph.D}} \\
        \vspace{0.251cm}

        Head of Economics and Experimentation \\
        {\bf{\large{Zalando SE}}} \\
        \textcolor{gray}{M\"{u}hlenstra{\ss}e 25\\
        Berlin 10243, Germany} \\
        \vspace{0.25cm}

        \href{mailto:christopher.gandrud@gmail.com}{christopher.gandrud@gmail.com}\\
        \href{https://github.com/christophergandrud}{github.com/christophergandrud}\\[0.25cm]

        ORCID: 0000-0003-4723-7585\\[0.25cm]

        \medskip\hrule height 1pt

        \vspace{0.5cm}

        \today

    \end{flushright}



\vspace{0.5cm}

%%%%%% Positions  %%%%%%%%%%%%%%
\section*{Work Experiences}

\subsection*{Zalando SE (from July 2017)}

\subsubsection*{Head of Economics and Experimentation (Economics Team Lead prior to January 2019)}

\begin{itemize}

  \item \textbf{Measuring the right things}: I lead a team of economists, data scientists, and product managers redeveloping the company's KPI framework and how we evaluate product investments.

  \item \textbf{Measuring incremental impact}: I lead the development of Zalando's A/B testing platform and broader program to enable teams throughout the company to measure their incremental impact with causal and Bayesian inference methods. I guide research into new statistical methods and their application in the Zalando business context.

  \item Previously, I led the development of Zalando's \textbf{real-time ad auction and machine learned content recommendation system}. We created a platform that dramatically expanded Zalando's on-site advertising business.

\end{itemize}

\subsection*{Harvard University Institute for Quantitative Social Science (2017)}

\subsubsection*{Research Fellow}

I led a team developing statistical software for academic and industry applications. 

\subsection*{City, University of London (2015-2018)}

\subsubsection*{Lecturer in Statistics and International Political Economy}

I was a Lecturer in international political economy (quantitative methods) in the Department of International Politics and the Q-Step Centre for quantitative social science education.

\subsection*{Hertie School of Governance (August 2013-June 2017)}

\subsubsection*{Post-Doctoral Fellow}

I coauthored with Prof. Mark Hallerberg a project examining the political economy of responses to financial crises. We were generously funded by the Deutsche Forschungsgemeinschaft (German National Research Foundation).\vspace{0.25cm}

\noindent I designed and taught a graduate-level course on collaborative data science and supervised masters theses.

\subsection*{Yonsei University (2012-2013)}
\subsubsection*{Lecturer in Statistics and International Political Economy}

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}


%%%%%%% Education %%%%%%%%%%%%%%
\section*{Eduction}

\subsection*{London School of Economics (2008-2012)}
\subsubsection*{MRes/PhD Political Science (Quantitative Research Methodology)}

\emph{Awarded MRes with Distinction} \\

\noindent My thesis used signalling games, event history analysis, and case studies to examine how economic policies are made in times of crisis.

\subsection*{London School of Economics (2005-2006)}
\subsubsection*{MSc Comparative Politics (Research Methodology)}

{\emph{Graduated with Distinction}}

\subsection*{McGill University (2003-2005)}
\subsubsection*{BA (Honours) Political Science \& Geography}

{\emph{Graduated with First Class Honours, in the top 10\% of the class}}

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

%%%%%%% Publications %%%%%%%%%%%%%%

\section*{Publications}

\subsection*{Published Peer Reviewed Articles}

\begin{itemize}

    \item Taking Time (and Space) Seriously: How Scholars Falsely Infer Policy Diffusion from Model Misspecification. With Cody A. Drolc and Laron K. Williams. 2021 \emph{Policy Studies Journal}. 49(2): 484-515.

    \item The Measurement of Real-Time Perceptions of Financial Stress: Implications for Political Science. With Mark Hallerberg. 2019. \emph{British Journal of Political Science}. 49(4): 1577-1589.

    \item The Reproducibility of Governance Indicators: Assessing Current Practices and Looking Forward. In \emph{Governance Indicators: Approaches, Progress, Promises}. 5th edition. 2018. Oxford: Oxford University Press.

    \item Explaining Variation and Change in Supervisory Confidentiality in the European Union. With Mark Hallerberg. 2018. \emph{West European Politics}. 41(4): 1025-1048.

    \item Financial Regulatory Transparency, International Institutions, and Sovereign Borrowing Costs. With Mark Copelovitch and Mark Hallerberg. 2018. \emph{International Studies Quarterly}. 62(1): 23-41.

    \item Simulating Probabilistic Long-Term Effects in Models with Temporal Dependence. With Laron K. Williams. 2017. \emph{R Journal}. 9(2): 401-408.

    \item Interpreting Fiscal Accounting Rules in the European Union. With Mark Hallerberg. 2017. \emph{Journal of European Public Policy}. 24(6): 832-851.

    \item Information and Financial Crisis Policy Making. With M\'{i}ch\'{e}al O'Keeffe. 2017. \emph{Journal of European Public Policy}. 24(3): 386-405.

    \item Statistical Agencies and Responses to Financial Crises: Eurostat, Bad Banks, and the ESM. With Mark Hallerberg. 2016. {\emph{West European Politics}}. 39(3): 545-564.

    \item Two Sword Lengths Apart: Credible commitment problems and physical violence in democratic national legislatures. 2016. \emph{Journal of Peace Research}. 53(1): 130-145.

        \begin{itemize}
            \item Interviewed about research on \href{http://www.cbc.ca/radio/day6/episode-286-parliamentary-brawls-transgender-rights-the-raptors-secret-weapon-migrant-ships-and-more-1.3591232/you-thought-elbowgate-was-bad-check-out-these-political-brawls-1.3591248}{CBC Radio 1}.

            \item Applied to understanding violence in the Turkish Parliament in \href{https://politicalviolenceataglance.org/2016/05/27/brawl-in-turkish-national-assembly-indicates-deeper-trouble/}{Political Violence @ a Glance}.

            \item Applied to understanding violence in the Ukrainian Parliament in \href{http://voxukraine.org/2015/12/24/causes-and-possible-solutions-to-brawling-in-the-ukrainian-parliament-en-2/}{VoxUkraine}.

            \item Write up on the \href{http://t.co/fETbFCXcYU}{Monkey Cage} with Emily Beaulieu.

        \end{itemize}

    \item Does Banking Union Worsen the EU's Democratic Deficit? The need for greater supervisory data transparency. With Mark Hallerberg. 2015. {\emph{Journal of Common Market Studies}}. 53(4):769-785.

        \begin{itemize}
            \item Data set updated through 2015 at \href{http://bruegel.org/2016/05/the-european-union-remains-a-laggard-on-banking-supervisory-transparency/}{Bruegel}.
        \end{itemize}

    \item When All is Said and Done: Updating `Elections, Special Interests, and Financial Crisis'. With Mark Hallerberg. 2015. \emph{Research and Politics}. 2(3):1-9.

    \item Inflated Expectations: How Government Partisanship Shapes Bureaucrats' Inflation Forecasts. With Cassandra Grafstr\"{o}m. 2015. {\emph{Political Science Research and Methods}}. 3(2):253-380.

    \begin{itemize}
        \item Write up on the \href{http://www.washingtonpost.com/blogs/monkey-cage/wp/2015/01/28/the-fed-cant-accurately-forecast-inflation-heres-why-this-may-hurt-democrats/}{Monkey Cage}.
    \end{itemize}

    \item simPH: An R Package for Illustrating Estimates from Cox Proportional Hazard Models Including for Interactive and Nonlinear Effects. 2015. {\emph{Journal of Statistical Software}}. 65(3):1-20.

    \item Letting German Banks Fail: Federalism and decisions to save troubled banks. With Sahil Deo, Christian Franz, and Mark Hallerberg. 2015 \emph{Politische Vierteljahresschrift} (PVS). 56(2): 159-181.

        \begin{itemize}
            \item Application of the theoretical framework to Austria published on the \href{https://www.weforum.org/agenda/2015/03/a-bank-bailout-lesson-from-austria/}{World Economic Forum}.
        \end{itemize}

    \item Competing Risks and the Mechanisms of Deposit Insurance Governance Convergence. 2014. {\emph{International Political Science Review}}. 35(2):197-217.

    \item The Diffusion of Financial Supervisory Governance Ideas. 2013. {\emph{Review of International Political Economy}}. 20(4):881-916.

\end{itemize}

\subsection*{Peer Reviewed Book}

\begin{itemize}
    \item Reproducible Research with R and RStudio. 2020. Third Edition. {\emph{Chapman \& Hall/CRC Press division of the Taylor \& Francis Group}}.

        \begin{itemize}
            \item First edition reviewed in \emph{The American Statistician}. 2014. 68(4):313--314.
        \end{itemize}

\end{itemize}

\subsection*{Other Published Academic/Policy Articles}

\begin{itemize}

    \item How Not to Create Zombie Banks: lessons for Italy from Japan. with Mark Hallerberg. \emph{Bruegel Policy Contribution}. March 2017.

    \item Visualize Dynamic Simulations of Autoregressive Relationships in R. With Laron K Williams and Guy D Whitten. \emph{The Political Methodologist}. 23(2): 6-10.

    \item Financial Regulatory Transparency: New data and implications for EU policy. With Mark Copelovitch and Mark Hallerberg. \emph{Bruegel Policy Contribution}. December 2015.

    \item Corrections and Refinements to the Database of Political Institutions' \textbf{yrcurnt} Election Timing Variable. 2015. {\emph{The Political Methodologist}}. 22(2): 2-4.

    \item Bad Banks in the EU: The impact of Eurostat rules. With Mark Hallerberg. \emph{Bruegel Working Paper}. 2014/15.

    \item Supervisory Transparency in the European Banking Union. With Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. January 2014.

    \item Who Decides?: Resolving Failed Banks in a European Framework. With Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. November 2013.

      \begin{itemize}
        \item Published in Polish as ``Kto decyduje? Mechanizm Restrukturyzacji i uporzadkowanej likwidacji bank\'{o}w w eropejskich ramach''. 2014. \emph{Nowa Europa}. 1(17): 114-141.
      \end{itemize}

    \item GitHub: A tool for Social Data Set Development and Verification in the Cloud. 2013. {\emph{The Political Methodologist}}. 20(2):2-7.

\end{itemize}

%%%%%%% Other Professional %%%%%%%%%%%%%%
\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Other Professional Activities}

\section*{Open Source Software}

\begin{itemize}
    \item spatialWeights: Calculate spatial weights for time-series cross-sectional data and report spatial clustering test statistics
    \item coreSim: Core functionality for simulating quantities of interest from generalised linear models.
    \item DataCombine: R tools for making it easier to combine and clean data sets.
    \item dpmr: Data package manager for R (with the Open Knowledge Foundation).
    \item dynsim: An R implementation of dynamic simulations of autoregressive relationships (with Laron K Williams and Guy D Whitten).
    \item imfr: R package for interacting with the International Monetary Fund's RESTful JSON API.
    \item networkD3: Tools for creating D3 JavaScript network graphs from R. With JJ Allaire and RStudio.
    \item plotMElm: Plot interaction marginal effects, including with false discovery rate confidence intervals, from linear models.
    \item pltesim: Simulate probabilistic long-term effects in models with temporal dependence (with Laron K Williams).
    \item repmis: A collection of miscellaneous tools for reproducible research with R.
    \item simPH: Tools for simulating and graphing quantities of interest estimated using Cox Proportional Hazards models.
\end{itemize}

%%%%%%%  Other Skills %%%%%%%%%%%%%%
\vspace{0.5cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Other Skills}

\subsection*{Programming and Machine Learning}

I am a highly skilled user of AWS, Bash, CSS, Git/GitHub, HTML, JavaScript, Julia, Jupyter, RMarkdown, LaTeX, Linux, SQL, Python, R, Shiny web apps, SPSS, Stan, and Stata.

\subsection*{Languages}

B1 German proficiency. I have also studied Korean, Spanish, and French. 


\end{document}
