\documentclass[a4paper]{article}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=cyan,
    urlcolor=cyan
}
\usepackage{url}
\usepackage[authoryear]{natbib}


\begin{document}

    \begin{flushright}
	    {\huge{Christopher Gandrud, Ph.D}} \\
        \vspace{0.25cm}

        Economics Lead \\
        {\bf{\large{Zalando SE}}} \\
        \textcolor{gray}{M\"{u}hlenstra{\ss}e 25\\
        Berlin 10243, Germany} \\
        \vspace{0.25cm}

        \href{mailto:christopher.gandrud@zalando.de}{christopher.gandrud@zalando.de}\\[0.25cm]

        ORCID: 0000-0003-4723-7585\\[0.25cm]

        \medskip\hrule height 1pt

        \vspace{0.5cm}

        \today

    \end{flushright}



\vspace{0.5cm}

%%%%%% Positions  %%%%%%%%%%%%%%
\section*{Work Experiences}

\subsection*{Zalando SE (from July 2017)}

\subsubsection*{Economics Lead}

I lead an international team of economists, machine learning experts, and backend engineers, researching, developing, and deploying cutting-edge systems for large scale decision-making. In particular, we are developing a real-time auction system for content placement on the Zalando website and leading an effort to improve attribution modelling.

\subsection*{Harvard University (2017)}

\subsubsection*{Research Fellow}

With Prof. Gary King, I developed statistical software and statistical software best practices for a wide range of social science applications.

\subsection*{City, University of London (since 2015)}

\subsubsection*{Lecturer}

I was a Lecturer in international political economy (quantitative methods) in the Department of International Politics and the Q-Step Centre.

\subsection*{Hertie School of Governance (August 2013-June 2017)}

\subsubsection*{Post-Doctoral Fellow}

I coauthored with Prof. Mark Hallerberg a project examining the political economy of responses to financial crises. We were generously funded by the Deutsche Forschungsgemeinschaft (German National Research Foundation).\vspace{0.25cm}

\noindent I designed and taught a graduate-level course on collaborative data science and supervise masters theses.

\subsection*{Yonsei University (2012-2013)}
\subsubsection*{Lecturer}

\subsection*{Hertie School of Governance (2010--2012)}
\subsubsection*{Research Associate}

\subsection*{London School of Economics (2010-2011)}
\subsubsection*{Fellow in Government}

\subsection*{London School of Economics/Peking University (August 2011 \& 2012)}
\subsubsection*{Graduate Teaching Assistant}

\subsection*{London School of Economics (2009-2012)}
\subsubsection*{Graduate Teaching Assistant}

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}


%%%%%%% Education %%%%%%%%%%%%%%
\section*{Eduction}

\subsection*{London School of Economics (2008-2012)}
\subsubsection*{MRes/PhD Political Science (Quantitative Research Methodology)}

\emph{Awarded MRes with Distinction} \\

\noindent My thesis used signalling games, event history analysis, and case studies to examine how economic policies are made in times of crisis.

\begin{itemize}
    \item Examiners: Charles Goodhart and Vera E. Troeger
    \item Supervisors: Cheryl Schonhardt-Bailey and Simon Hix
\end{itemize}

\subsection*{London School of Economics (2005-2006)}
\subsubsection*{MSc Comparative Politics (Research Methodology)}

{\emph{Graduated with Distinction}}

\subsection*{McGill University (2003-2005)}
\subsubsection*{BA (Honours) Political Science \& Geography}

{\emph{Graduated with First Class Honours, in the top 10\% of the class}}

\section*{Other Education}

\subsection*{Oxford University Spring Summer School (2014)}

\subsubsection*{Bayesian Hierarchical Models for Social Research (taught by Jeff Gill)}

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

%%%%%%% Publications %%%%%%%%%%%%%%

\section*{Publications}

\noindent Papers and book chapters from my research program can be downloaded from {\url{http://bit.ly/1HQAi9I}}.

\subsection*{Published Peer Reviewed Articles}

\begin{itemize}


    \item Explaining Variation and Change in Supervisory Confidentiality in the European Union. With Mark Hallerberg. Forthcoming at \emph{West European Politics}.

    \item The Measurement of Real-Time Perceptions of Financial Stress: Implications for political science. With Mark Hallerberg. Forthcoming at \emph{British Journal of Political Science}.

    \item Financial Regulatory Transparency, International Institutions, and Sovereign Borrowing Costs. With Mark Copelovitch and Mark Hallerberg. Forthcoming at \emph{International Studies Quarterly}.

    \item Simulating Probabilistic Long-Term Effects in Models with Temporal Dependence. With Laron K. Williams. 2017. \emph{R Journal}. 9(2): 401-408.

    \item Interpreting Fiscal Accounting Rules in the European Union. With Mark Hallerberg. 2017. \emph{Journal of European Public Policy}. 24(6): 832-851.

    \item Information and Financial Crisis Policy Making. With M\'{i}ch\'{e}al O'Keeffe. 2017. \emph{Journal of European Public Policy}. 24(3): 386-405.

    \item Statistical Agencies and Responses to Financial Crises: Eurostat, Bad Banks, and the ESM. With Mark Hallerberg. 2016. {\emph{West European Politics}}. 39(3): 545-564.

    \item Two Sword Lengths Apart: Credible commitment problems and physical violence in democratic national legislatures. 2016. \emph{Journal of Peace Research}. 53(1): 130-145.

        \begin{itemize}
            \item Interviewed about research on \href{http://www.cbc.ca/radio/day6/episode-286-parliamentary-brawls-transgender-rights-the-raptors-secret-weapon-migrant-ships-and-more-1.3591232/you-thought-elbowgate-was-bad-check-out-these-political-brawls-1.3591248}{CBC Radio 1}.

            \item Applied to understanding violence in the Turkish Parliament in \href{https://politicalviolenceataglance.org/2016/05/27/brawl-in-turkish-national-assembly-indicates-deeper-trouble/}{Political Violence @ a Glance}.

            \item Applied to understanding violence in the Ukrainian Parliament in \href{http://voxukraine.org/2015/12/24/causes-and-possible-solutions-to-brawling-in-the-ukrainian-parliament-en-2/}{VoxUkraine}.

            \item Write up on the \href{http://t.co/fETbFCXcYU}{Monkey Cage} with Emily Beaulieu.

        \end{itemize}

    \item Does Banking Union Worsen the EU's Democratic Deficit? The need for greater supervisory data transparency. With Mark Hallerberg. 2015. {\emph{Journal of Common Market Studies}}. 53(4):769-785.

        \begin{itemize}
            \item Data set updated through 2015 at \href{http://bruegel.org/2016/05/the-european-union-remains-a-laggard-on-banking-supervisory-transparency/}{Bruegel}.
        \end{itemize}

    \item When All is Said and Done: Updating `Elections, Special Interests, and Financial Crisis'. With Mark Hallerberg. 2015. \emph{Research and Politics}. 2(3):1-9.

    \item Inflated Expectations: How Government Partisanship Shapes Bureaucrats' Inflation Forecasts. With Cassandra Grafstr\"{o}m. 2015. {\emph{Political Science Research and Methods}}. 3(2):253-380.

    \begin{itemize}
        \item Write up on the \href{http://www.washingtonpost.com/blogs/monkey-cage/wp/2015/01/28/the-fed-cant-accurately-forecast-inflation-heres-why-this-may-hurt-democrats/}{Monkey Cage}.
    \end{itemize}

    \item simPH: An R Package for Illustrating Estimates from Cox Proportional Hazard Models Including for Interactive and Nonlinear Effects. 2015. {\emph{Journal of Statistical Software}}. 65(3):1-20.

    \item Letting German Banks Fail: Federalism and decisions to save troubled banks. With Sahil Deo, Christian Franz, and Mark Hallerberg. 2015 \emph{Politische Vierteljahresschrift} (PVS). 56(2): 159-181.

        \begin{itemize}
            \item Application of the theoretical framework to Austria published on the \href{https://www.weforum.org/agenda/2015/03/a-bank-bailout-lesson-from-austria/}{World Economic Forum}.
        \end{itemize}

    \item Competing Risks and the Mechanisms of Deposit Insurance Governance Convergence. 2014. {\emph{International Political Science Review}}. 35(2):197-217.

    \item The Diffusion of Financial Supervisory Governance Ideas. 2013. {\emph{Review of International Political Economy}}. 20(4):881-916.

\end{itemize}

\subsection*{Peer Reviewed Book}

\begin{itemize}
    \item Reproducible Research with R and RStudio. 2015. Second Edition {\emph{Chapman \& Hall/CRC Press division of the Taylor \& Francis Group}}.

        \begin{itemize}
            \item First edition reviewed in \emph{The American Statistician}. 2014. 68(4):313--314.
        \end{itemize}

\end{itemize}

\subsection*{Other Published Academic/Policy Articles}

\begin{itemize}

    \item The Reproducibility of Governance Indicators: Assessing Current Practices and Looking Forward. Forthcoming in the \emph{Hertie Governance Report: 2017}. Oxford: Oxford University Press.

    \item How Not to Create Zombie Banks: lessons for Italy from Japan. with Mark Hallerberg. \emph{Bruegel Policy Contribution}. March 2017.

    \item Visualize Dynamic Simulations of Autoregressive Relationships in R. With Laron K Williams and Guy D Whitten. \emph{The Political Methodologist}. 23(2): 6-10.

    \item Financial Regulatory Transparency: New data and implications for EU policy. With Mark Copelovitch and Mark Hallerberg. \emph{Bruegel Policy Contribution}. December 2015.

    \item Corrections and Refinements to the Database of Political Institutions' \textbf{yrcurnt} Election Timing Variable. 2015. {\emph{The Political Methodologist}}. 22(2): 2-4.

    \item Bad Banks in the EU: The impact of Eurostat rules. With Mark Hallerberg. \emph{Bruegel Working Paper}. 2014/15.

    \item Supervisory Transparency in the European Banking Union. With Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. January 2014.

    \item Who Decides?: Resolving Failed Banks in a European Framework. With Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. November 2013.

      \begin{itemize}
        \item Published in Polish as ``Kto decyduje? Mechanizm Restrukturyzacji i uporzadkowanej likwidacji bank\'{o}w w eropejskich ramach''. 2014. \emph{Nowa Europa}. 1(17): 114-141.
      \end{itemize}

    \item GitHub: A tool for Social Data Set Development and Verification in the Cloud. 2013. {\emph{The Political Methodologist}}. 20(2):2-7.

\end{itemize}


\section*{Under Review/Working Papers/Work in Progress}

\begin{itemize}

    \item Taking Time (and Space) Seriously: The Ins and Outs of Temporally-Lagged Spatial-Lag Variables. With Cody A. Drolc and Laron K. Williams.

    \item Predicting Self-fulfilling Financial Crises. With Thomas Pepinsky.

    \item Bad Banks as a Response to Crises: When Do Governments Use Them, and Why Does Their Governance Differ? With Mark Hallerberg.

    \item Speaking Under Stress: An Analysis of Federal Reserve Speeches. With Kevin Young.

    \item Creating Scrutiny Indicators: A Change Point Exploration of Congressional Scrutiny of the US Federal Reserve. With Kevin Young.

    \item On Whose Account? Financial Crises, Elections, and the Rules of the Game. Book project with Mark Hallerberg.

    \item Pulling the Trigger: When do governments use macro-prudential policies? With Jeff Chwieroth.

    \item Fed Governors' Predictions: Professional background and Partisan Affiliation

\end{itemize}

%%%%%%% Teaching %%%%%%%%%%%%%%

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Teaching}

\subsection*{City University London (Lecturer)}

\begin{itemize}
    \item IP2038: Data Analysis in the Real-World
    \item SG1021: Lies, Damn Lies, and Statistics
    \item SG1022: Producing Social Data
\end{itemize}

\subsection*{Hertie School of Governance (Guest Lecturer)}

\begin{itemize}

    \item MPP-E1180: Introduction to Collaborative Social Science Data Analysis

\end{itemize}

\subsection*{Yonsei University (Lecturer)}

\begin{itemize}

    \item INT3042: Introduction to Social Science Data Analysis
    \item NT4021: The Global Monetary \& Financial System
    \item EIC3120: International Political Economy
    \item INT3041: War, Peacebuilding, and Reconstruction
    \item INT3040: Understanding Global Affairs

\end{itemize}

\subsection*{London School of Economics (Fellow or Teaching Assistant)}

\begin{itemize}
    \item MI452: Applied Regression Analysis
    \item MI451: Introduction to Quantitative Analysis
    \item GV101: Introduction to Comparative Politics
    \item FN208: Post-Crisis: What Next for the International Financial and Monetary Systems? (LSE-Peking University Summer School)
\end{itemize}

%%%%%%% Conference Presentations %%%%%%%%%%%%%%
\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Conference Presentations/Invited Talks}

\begin{itemize}
    \item American Political Science Association Annual Conference (2012--2017)
    \item European Political Science Association Annual Conference (2011/2014/2016/2017)
    \item LSE Systemic Risk Centre Conference (2016)
    \item School of Politics and International Relations Research Seminar, University of Kent (2016)
    \item International Political Economy Society Conference (2013/2015/2016)
    \item Politics of Secrecy Workshop, University of Munich (2016)
    \item Universit\'{e} de Montr\'{e}al political science talk.
    \item Bank of Iceland: Capital Flows, Systemic Risk, and Policy Responses Conference (2016)
    \item Freie Universit\"{a}t Berlin: Financial Crisis Workshop (2016)
    \item University of Mannheim: Political Forecasting (2015)
    \item Texas A \& M University: Political Budgeting Across Europe (2015)
    \item Open Energy Modeling Workshop (2015)
    \item Political Economy of International Organizations (2015)
    \item Princeton University: Monetary Policy and Central Banking: Historical analysis and contemporary approaches (2015)
    \item Banking Regulation and Supervision and the Great Leap Forward in European Integration, Brussels (2014)
    \item University of Mannheim: Textual Analysis in the Social Sciences (2014)
    \item YoungDNB Seminar on Transparency, Bank of the Netherlands (2014)
    \item csv,Conf (2014)
    \item Midwestern Political Science Association Annual Conference (2012/2014)
    \item CESifo Area Conference on Macro, Money, and International Finance (2014)
    \item International Studies Association Annual Convention (2012/2013)
    \item Waseda University GLOPE II Conference on Political Institutions (2012)
    \item Korean Political Science Association World Congress (2011)
    \item ECPR Regulation in the Age of Crisis (2010)
\end{itemize}


%%%%%%% Other Professional %%%%%%%%%%%%%%
\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Other Professional Activities}

\section*{Software}

\begin{itemize}
    \item spatialWeights: Calculate spatial weights for time-series cross-sectional data and report spatial clustering test statistics
    \item coreSim: Core functionality for simulating quantities of interest from generalised linear models.
    \item DataCombine: R tools for making it easier to combine and clean data sets.
    \item dpmr: Data package manager for R (with the Open Knowledge Foundation).
    \item dynsim: An R implementation of dynamic simulations of autoregressive relationships (with Laron K Williams and Guy D Whitten).
    \item imfr: R package for interacting with the International Monetary Fund's RESTful JSON API.
    \item networkD3: Tools for creating D3 JavaScript network graphs from R. With JJ Allaire and RStudio.
    \item plotMElm: Plot interaction marginal effects, including with false discovery rate confidence intervals, from linear models.
    \item pltesim: Simulate probabilistic long-term effects in models with temporal dependence (with Laron K Williams).
    \item repmis: A collection of miscellaneous tools for reproducible research with R.
    \item simPH: Tools for simulating and graphing quantities of interest estimated using Cox Proportional Hazards models.
\end{itemize}

\subsection*{Reviewer}

American Political Science Review, Business and Politics, Chapman \& Hall/CRC Press, Economics and Politics,
International Political Science Review, International Studies Perspectives,
International Studies Quarterly,
Journal of Common Market Studies, Journal of Statistical Software,
Managerial Finance, Manning Publications Co.,
Packt Publishing, Political Science Research and Methods, Political Research
Quarterly, Regulation and Governance, Review of International Political Economy,
Routledge, Sage Publishing, Scientific Data, West European Politics.

\subsection*{Professional Memberships}

I am or have been a member of the Foundation for Open Access Research, American Political Science Association, the European Political Science Association, and the Midwest Political Science Association, rOpenGov.

\section*{External Funding/Awards}

\begin{itemize}

    \item European Research Council Horizon 2020 (1.5 million Euros, Ronen Palan principal investigator)
    \item LSE IR Department Seed Grant (with Jeff Chwieroth)
    \item Project grant (270,000 Euros) from the Deutsche Forschungsgemeinschaft (with Mark Hallerberg)
    \item LSE Class Teacher Award, Quantitative Methodology (2009-2010)
    \item LSE Government Department PhD Studentship (2008-2012)
    \item Penn State University President's Award
    \item Canadian Tower Scholarship for the Environment

\end{itemize}

%%%%%%%  Other Skills %%%%%%%%%%%%%%
\vspace{0.5cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Other Skills}

\subsection*{IT}

I am a highly skilled user of AWS, Bash, CSS, Git/GitHub, HTML, JAGS, JavaScript, Julia, knitr, LaTeX, Linux, Lyx, MS Office, MySQL, Python, R, Shiny web apps, SPSS, Stan, and Stata.

\subsection*{Languages}

I have studied Spanish, French, Korean, and am currently working on German.

%%%%%% References %%%%%%%%%%%%%%%%%%%%

\vspace{0.5cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{References}

\noindent \textbf{Prof. Gary King} \\
1737 Cambridge Street \\
Harvard University \\
Cambridge, MA 02138
USA \\
\href{mailto:king@harvard.edu}{king@harvard.edu}\\

\noindent \textbf{Prof. Mark Hallerberg} \\
Hertie School of Governance\\
Friedrichstra{\ss}e 180\\
Berlin 10117, Germany \\
+49 (0)30 259 219 307 \\
\href{mailto:hallerberg@hertie-school.com}{hallerberg@hertie-school.com}\\

\noindent \textbf{Prof. Jeff Chwieroth}\\
Department of International Relations \\
London School of Economics \\
Houghton Street \\
London WC2A 2AE \\
United Kingdom\\
+44 (0) 20 7955 7209\\
\href{mailto:j.m.chwieroth@lse.ac.uk}{j.m.chwieroth@lse.ac.uk}\\

\noindent \textbf{Prof. Simon Hix}\\
Government Department \\
London School of Economics \\
Houghton Street \\
London WC2A 2AE \\
United Kingdom\\
+44 (0) 20 7955 7657\\
\href{mailto:s.hix@lse.ac.uk}{s.hix@lse.ac.uk}\\

\noindent \textbf{Prof. Cheryl Schonhardt-Bailey}\\
Government Department \\
London School of Economics \\
Houghton Street \\
London WC2A 2AE \\
United Kingdom\\
+44 (0) 20 7955 7187\\
\href{mailto:c.m.schonhardt-bailey@lse.ac.uk}{c.m.schonhardt-bailey@lse.ac.uk}\\

\end{document}
