\documentclass[a4paper]{article}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=cyan,
    urlcolor=cyan
}
\usepackage{url}
\usepackage[authoryear]{natbib}


\begin{document}

    \begin{flushright}
        {\huge{Christopher Gandrud, Ph.D}} \\
        \vspace{0.251cm}

        Head of Economics and Experimentation \\
        {\bf{\large{Zalando SE}}} \\
        \textcolor{gray}{M\"{u}hlenstra{\ss}e 25\\
        Berlin 10243, Germany} \\
        \vspace{0.25cm}

        \href{mailto:christopher.gandrud@gmail.com}{christopher.gandrud@gmail.com}\\
        \href{https://github.com/christophergandrud}{github.com/christophergandrud}\\[0.25cm]

        ORCID: 0000-0003-4723-7585\\[0.25cm]

        \medskip\hrule height 1pt

        \vspace{0.5cm}

        \today

    \end{flushright}



\vspace{0.5cm}

%%%%%% Positions  %%%%%%%%%%%%%%
\section*{Beruflicher Wedegang}

\subsection*{Zalando SE, Berlin (ab July 2017)}

\subsubsection*{Leiter von Wirtschaft und Experimente}

\subsection*{Harvard University Institute for Quantitative Social Science, Cambridge USA (2017)}

\subsubsection*{Forschungswissenschaftler}

\subsection*{City, University of London (2015-2018)}

\subsubsection*{Dozent}

\subsection*{Hertie School of Governance, Berlin (August 2013-Juni 2017)}

\subsubsection*{Postdoktorand}

\subsection*{Yonsei University, S\"{u}dkorea (2012-2013)}
\subsubsection*{Dozent}

\subsection*{Hertie School of Governance, Berlin (2010--2012)}
\subsubsection*{Wissenschaftlicher Mitarbeiter}

\subsection*{London School of Economics (2010-2011)}
\subsubsection*{Wissenschaftlicher Mitarbeiter}

\subsection*{London School of Economics/Peking University (August 2011 \& 2012)}
\subsubsection*{Diplom-Lehrassistent}

\subsection*{London School of Economics (2009-2012)}
\subsubsection*{Diplom-Lehrassistent}

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}


%%%%%%% Education %%%%%%%%%%%%%%
\section*{Ausbildung}

\subsection*{London School of Economics (2008-2012)}
\subsubsection*{MRes/PhD Political Science Quantitative Research Methodology (MRes/PhD in Politikwissenschaft und Statistik))}

\emph{mit Distinction} \\

\subsection*{London School of Economics (2005-2006)}
\subsubsection*{MSc Comparative Politics Research Methodology (Master in Wissenschaften))}

{\emph{mit Distinction}}

\subsection*{McGill University (2003-2005)}
\subsubsection*{BA (Honours) Political Science \& Geography (Bachelorabschluss in Politikwissenschaft und Geographie)}

{\emph{First Class Honours (in den Top 10\% der Klasse)}}

\subsection*{Northwestern Pennsylvania Collegiate Academy (1998-2002)}
\subsubsection*{Sekundarschulabschluss (äquivalent zu Abitur)}

{\emph{Summa Cum Laude}}


\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

%%%%%%% Publications %%%%%%%%%%%%%%

\section*{Veröffentlichungen}

\begin{itemize}

    \item Taking Time (and Space) Seriously: How Scholars Falsely Infer Policy Diffusion from Model Misspecification. mit Cody A. Drolc and Laron K. Williams. Forthcoming at \emph{Policy Studies Journal}.

    \item The Measurement of Real-Time Perceptions of Financial Stress: Implications for Political Science. mit Mark Hallerberg. 2019. \emph{British Journal of Political Science}. 49(4): 1577-1589.

    \item The Reproducibility of Governance Indicators: Assessing Current Practices and Looking Forward. In \emph{Governance Indicators: Approaches, Progress, Promises}. 5th edition. 2018. Oxford: Oxford University Press.

    \item Explaining Variation and Change in Supervisory Confidentiality in the European Union. mit Mark Hallerberg. 2018. \emph{West European Politics}. 41(4): 1025-1048.

    \item Financial Regulatory Transparency, International Institutions, and Sovereign Borrowing Costs. mit Mark Copelovitch and Mark Hallerberg. 2018. \emph{International Studies Quarterly}. 62(1): 23-41.

    \item Simulating Probabilistic Long-Term Effects in Models mit Temporal Dependence. mit Laron K. Williams. 2017. \emph{R Journal}. 9(2): 401-408.

    \item Interpreting Fiscal Accounting Rules in the European Union. mit Mark Hallerberg. 2017. \emph{Journal of European Public Policy}. 24(6): 832-851.

    \item Information and Financial Crisis Policy Making. mit M\'{i}ch\'{e}al O'Keeffe. 2017. \emph{Journal of European Public Policy}. 24(3): 386-405.

    \item Statistical Agencies and Responses to Financial Crises: Eurostat, Bad Banks, and the ESM. mit Mark Hallerberg. 2016. {\emph{West European Politics}}. 39(3): 545-564.

    \item Two Sword Lengths Apart: Credible commitment problems and physical violence in democratic national legislatures. 2016. \emph{Journal of Peace Research}. 53(1): 130-145.

        \begin{itemize}
            \item Interviewed about research on \href{http://www.cbc.ca/radio/day6/episode-286-parliamentary-brawls-transgender-rights-the-raptors-secret-weapon-migrant-ships-and-more-1.3591232/you-thought-elbowgate-was-bad-check-out-these-political-brawls-1.3591248}{CBC Radio 1}.

            \item Applied to understanding violence in the Turkish Parliament in \href{https://politicalviolenceataglance.org/2016/05/27/brawl-in-turkish-national-assembly-indicates-deeper-trouble/}{Political Violence @ a Glance}.

            \item Applied to understanding violence in the Ukrainian Parliament in \href{http://voxukraine.org/2015/12/24/causes-and-possible-solutions-to-brawling-in-the-ukrainian-parliament-en-2/}{VoxUkraine}.

            \item Write up on the \href{http://t.co/fETbFCXcYU}{Monkey Cage} mit Emily Beaulieu.

        \end{itemize}

    \item Does Banking Union Worsen the EU's Democratic Deficit? The need for greater supervisory data transparency. mit Mark Hallerberg. 2015. {\emph{Journal of Common Market Studies}}. 53(4):769-785.

        \begin{itemize}
            \item Data set updated through 2015 at \href{http://bruegel.org/2016/05/the-european-union-remains-a-laggard-on-banking-supervisory-transparency/}{Bruegel}.
        \end{itemize}

    \item When All is Said and Done: Updating `Elections, Special Interests, and Financial Crisis'. mit Mark Hallerberg. 2015. \emph{Research and Politics}. 2(3):1-9.

    \item Inflated Expectations: How Government Partisanship Shapes Bureaucrats' Inflation Forecasts. mit Cassandra Grafstr\"{o}m. 2015. {\emph{Political Science Research and Methods}}. 3(2):253-380.

    \begin{itemize}
        \item Write up on the \href{http://www.washingtonpost.com/blogs/monkey-cage/wp/2015/01/28/the-fed-cant-accurately-forecast-inflation-heres-why-this-may-hurt-democrats/}{Monkey Cage}.
    \end{itemize}

    \item simPH: An R Package for Illustrating Estimates from Cox Proportional Hazard Models Including for Interactive and Nonlinear Effects. 2015. {\emph{Journal of Statistical Software}}. 65(3):1-20.

    \item Letting German Banks Fail: Federalism and decisions to save troubled banks. mit Sahil Deo, Christian Franz, and Mark Hallerberg. 2015 \emph{Politische Vierteljahresschrift} (PVS). 56(2): 159-181.

        \begin{itemize}
            \item Application of the theoretical framework to Austria published on the \href{https://www.weforum.org/agenda/2015/03/a-bank-bailout-lesson-from-austria/}{World Economic Forum}.
        \end{itemize}

    \item Competing Risks and the Mechanisms of Deposit Insurance Governance Convergence. 2014. {\emph{International Political Science Review}}. 35(2):197-217.

    \item The Diffusion of Financial Supervisory Governance Ideas. 2013. {\emph{Review of International Political Economy}}. 20(4):881-916.

\end{itemize}

\subsection*{Bucher}

\begin{itemize}
    \item Reproducible Research with R and RStudio. 2020. Third Edition. {\emph{Chapman \& Hall/CRC Press division of the Taylor \& Francis Group}}.
\end{itemize}

\subsection*{Andere Veröffentlichungen}

\begin{itemize}

    \item How Not to Create Zombie Banks: lessons for Italy from Japan. mit Mark Hallerberg. \emph{Bruegel Policy Contribution}. March 2017.

    \item Visualize Dynamic Simulations of Autoregressive Relationships in R. mit Laron K Williams and Guy D Whitten. \emph{The Political Methodologist}. 23(2): 6-10.

    \item Financial Regulatory Transparency: New data and implications for EU policy. mit Mark Copelovitch and Mark Hallerberg. \emph{Bruegel Policy Contribution}. December 2015.

    \item Corrections and Refinements to the Database of Political Institutions' \textbf{yrcurnt} Election Timing Variable. 2015. {\emph{The Political Methodologist}}. 22(2): 2-4.

    \item Bad Banks in the EU: The impact of Eurostat rules. mit Mark Hallerberg. \emph{Bruegel Working Paper}. 2014/15.

    \item Supervisory Transparency in the European Banking Union. mit Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. January 2014.

    \item Who Decides?: Resolving Failed Banks in a European Framework. mit Mark Hallerberg. {\emph{Bruegel Policy Contribution}}. November 2013.

      \begin{itemize}
        \item Published in Polish as ``Kto decyduje? Mechanizm Restrukturyzacji i uporzadkowanej likwidacji bank\'{o}w w eropejskich ramach''. 2014. \emph{Nowa Europa}. 1(17): 114-141.
      \end{itemize}

    \item GitHub: A tool for Social Data Set Development and Verification in the Cloud. 2013. {\emph{The Political Methodologist}}. 20(2):2-7.

\end{itemize}

%%%%%%% Teaching %%%%%%%%%%%%%%

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Lehren}

\subsection*{RTG DYNAMICS (Humboldt/Hertie)}

\begin{itemize}
    \item Programming Methods for Data Retrieval \& Management
\end{itemize}

\subsection*{Harvard University (Short courses)}

\begin{itemize}
    \item Developing Statistical Software Using IQSS Best Practices
    \item Tools for Reproducible Data Science
    \item Dynamic Web Documents with Dashboards and Shiny (with Dustin Tingley)
\end{itemize}

\subsection*{City University London (Lecturer)}

\begin{itemize}
    \item IP2038: Data Analysis in the Real-World
    \item SG1021: Lies, Damn Lies, and Statistics
    \item SG1022: Producing Social Data
\end{itemize}

\subsection*{Hertie School of Governance (Guest Lecturer)}

\begin{itemize}

    \item MPP-E1180: Introduction to Collaborative Social Science Data Analysis

\end{itemize}

\subsection*{Yonsei University (Lecturer)}

\begin{itemize}

    \item INT3042: Introduction to Social Science Data Analysis
    \item NT4021: The Global Monetary \& Financial System
    \item EIC3120: International Political Economy
    \item INT3041: War, Peacebuilding, and Reconstruction
    \item INT3040: Understanding Global Affairs

\end{itemize}

\subsection*{London School of Economics (Fellow or Teaching Assistant)}

\begin{itemize}
    \item MI452: Applied Regression Analysis
    \item MI451: Introduction to Quantitative Analysis
    \item GV101: Introduction to Comparative Politics
    \item FN208: Post-Crisis: What Next for the International Financial and Monetary Systems? (LSE-Peking University Summer School)
\end{itemize}

%%%%%%% Conference Presentations %%%%%%%%%%%%%%
\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Konferenzpr\"{a}sentation}

\begin{itemize}
    \item Berlin AI Mondays (2020)    
    \item PyData Berlin (2018)
    \item American Political Science Association Annual Conference (2012--2017)
    \item European Political Science Association Annual Conference (2011/2014/2016/2017)
    \item LSE Systemic Risk Centre Conference (2016)
    \item School of Politics and International Relations Research Seminar, University of Kent (2016)
    \item International Political Economy Society Conference (2013/2015/2016)
    \item Politics of Secrecy Workshop, University of Munich (2016)
    \item Universit\'{e} de Montr\'{e}al political science talk.
    \item Bank of Iceland: Capital Flows, Systemic Risk, and Policy Responses Conference (2016)
    \item Freie Universit\"{a}t Berlin: Financial Crisis Workshop (2016)
    \item University of Mannheim: Political Forecasting (2015)
    \item Texas A \& M University: Political Budgeting Across Europe (2015)
    \item Open Energy Modeling Workshop (2015)
    \item Political Economy of International Organizations (2015)
    \item Princeton University: Monetary Policy and Central Banking: Historical analysis and contemporary approaches (2015)
    \item Banking Regulation and Supervision and the Great Leap Forward in European Integration, Brussels (2014)
    \item University of Mannheim: Textual Analysis in the Social Sciences (2014)
    \item YoungDNB Seminar on Transparency, Bank of the Netherlands (2014)
    \item csv,Conf (2014)
    \item Midwestern Political Science Association Annual Conference (2012/2014)
    \item CESifo Area Conference on Macro, Money, and International Finance (2014)
    \item International Studies Association Annual Convention (2012/2013)
    \item Waseda University GLOPE II Conference on Political Institutions (2012)
    \item Korean Political Science Association World Congress (2011)
    \item ECPR Regulation in the Age of Crisis (2010)
\end{itemize}


%%%%%%% Other Professional %%%%%%%%%%%%%%
\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

\section*{Andere Beruflicher Wedegang}

\section*{Software-Entwicklung}

\begin{itemize}
    \item spatialWeights: Calculate spatial weights for time-series cross-sectional data and report spatial clustering test statistics
    \item coreSim: Core functionality for simulating quantities of interest from generalised linear models.
    \item DataCombine: R tools for making it easier to combine and clean data sets.
    \item dpmr: Data package manager for R (with the Open Knowledge Foundation).
    \item dynsim: An R implementation of dynamic simulations of autoregressive relationships (with Laron K Williams and Guy D Whitten).
    \item imfr: R package for interacting with the International Monetary Fund's RESTful JSON API.
    \item networkD3: Tools for creating D3 JavaScript network graphs from R. With JJ Allaire and RStudio.
    \item plotMElm: Plot interaction marginal effects, including with false discovery rate confidence intervals, from linear models.
    \item pltesim: Simulate probabilistic long-term effects in models with temporal dependence (with Laron K Williams).
    \item repmis: A collection of miscellaneous tools for reproducible research with R.
    \item simPH: Tools for simulating and graphing quantities of interest estimated using Cox Proportional Hazards models.
\end{itemize}

\subsection*{Reviewer}

American Political Science Review, Business and Politics, Chapman \& Hall/CRC Press, Economics and Politics,
International Political Science Review, International Studies Perspectives,
International Studies Quarterly,
Journal of Common Market Studies, Journal of Economic Policy Reform, Journal of Statistical Software,
Managerial Finance, Manning Publications Co.,
Packt Publishing, Political Science Research and Methods, Political Research
Quarterly, Regulation and Governance, Review of International Political Economy,
Routledge, Sage Publishing, Scientific Data, West European Politics.

\section*{Forschungsförderung}

\begin{itemize}

    \item European Research Council Horizon 2020 (1.5 million Euros, Ronen Palan principal investigator)
    \item LSE IR Department Seed Grant (with Jeff Chwieroth)
    \item Project grant (270,000 Euros) from the Deutsche Forschungsgemeinschaft (with Mark Hallerberg)
    \item LSE Class Teacher Award, Quantitative Methodology (2009-2010)
    \item LSE Government Department PhD Studentship (2008-2012)
    \item Penn State University President's Award
    \item Canadian Tower Scholarship for the Environment

\end{itemize}

\end{document}
