\documentclass[a4paper]{article}
\usepackage{color}
\usepackage{xcolor}
\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=cyan,
    urlcolor=cyan
}
\usepackage{url}
\usepackage[authoryear]{natbib}

\begin{document}

\begin{flushright}
    {\huge Christopher Gandrud, Ph.D} \\
    \vspace{0.251cm}

    Director of Data Science, PZN Surfaces \\
    {\bf{\large Spotify}} \\
    \vspace{0.25cm}

    \href{mailto:christopher.gandrud@gmail.com}{christopher.gandrud@gmail.com} \\
    \href{https://github.com/christophergandrud}{github.com/christophergandrud} \\
    \medskip\hrule height 1pt

    \vspace{0.5cm}
    \today
\end{flushright}

\vspace{0.5cm}

%%%%%% Positions  %%%%%%%%%%%%%%
\section*{Work Experience}

\noindent I lead cross-functional initiatives and data science organizations delivering AI personalization at scale---leading through example high-impact cultures where we make it happen together. I fly high---connecting dots across the business, communicating effectively with stakeholders from engineers to executives, and securing alignment on strategy. I dive deep into technical details and roadmaps, ensuring we prioritize the highest-value work and unblocking teams to ship. Track record: Spotify Home personalization, multi-year strategy definition with executive reporting, A/B testing platforms (hundreds of concurrent experiments), cross-functional organizations at Zalando with company-scale impact, and building healthy, resilient teams through change (high engagement scores post-reorganizations). 

\subsection*{Spotify (2022-present)}

\subsubsection*{Director of Data Science (2023-Present)}

I lead data scientists and analytics engineers accountable for Spotify's Home and personalization surfaces---the flagship experience approaching 600 million weekly active users. I drive cross-functional Company Bet initiatives with ML engineering, product, and design partners. Key initiatives include: \\

\begin{itemize}
    \item \textbf{Home Surface Strategy \& Execution}: Own the data science vision for Spotify's Home---the primary surface connecting fans with personalized content. Partner with cross-functional leadership to define roadmaps, then roll up sleeves to review analyses, debug pipelines, and ensure we ship high-quality outcomes that balance user value, creator outcomes, and business goals.
    \item \textbf{AI Personalization at Scale}: Lead teams building AI evaluation systems (e.g. LLMs as Judges) and refining ML reward functions across Spotify's generative recommendation systems. Drive measurable improvements in personalization quality serving hundreds of millions of daily users.
    \item \textbf{Metrics \& Business Impact}: Built company-level measurement frameworks connecting product metrics to retention and revenue. Own studio and mission-level metrics reporting, enabling data-driven prioritization and accelerating executive decision velocity.
    \item \textbf{New Format Discovery}: Led initiatives driving substantial growth in user discovery and engagement with emerging content formats (video, podcasts), directly contributing to platform-wide retention and creator ecosystem health.
\end{itemize}

\subsubsection*{Senior Insights Leader (2022-2023)}

Guided distributed teams of data scientists and user researchers developing personalization algorithms for Spotify Home, establishing foundations for impression economics and content distribution strategy.

\subsection*{Zalando SE (2017-2022)}

I built and led a cross-functional organization of engineers, product managers, data scientists, and economists across European locations, developing scalable platforms and ML systems that drove hundreds of millions of euros in measurable business impact.

\subsubsection*{Director of Economics and Experimentation (2020-2022, Head 2019-2020)}

Led a Studio-scale organization of managers across engineering, data science, and product with a ``one team, make it happen'' culture:

\begin{itemize}
    \item \textbf{Experimentation Platform at Scale}: Built Zalando's A/B testing infrastructure supporting hundreds of concurrent experiments, enabling rapid iteration and high-quality decision-making across the organization. Established measurement practices that became company standard.
    \item \textbf{Causal ML Software and Research Program}: Led development of causal machine learning methods and tools to measure incremental impact, driving rigorous evaluation of product and marketing investments.
    \item \textbf{Company KPI Framework}: Defined and operationalized company-wide customer-centric metrics, securing C-suite alignment while personally validating the underlying data pipelines and statistical methodology. Translated complex analytical concepts into actionable strategies for stakeholders from interns to executives.
\end{itemize}

\subsubsection*{Economics Head (2017-2019)}

Founded and scaled a cross-functional team (economists, engineers, product managers) that built Zalando's real-time ML-powered content recommendation and automated auction systems, generating hundreds of millions of euros in advertising revenue while improving customer content relevance and diversity.

\subsection*{Academic \& Open Source Leadership (2012-2017)}

Lecturer and Research Fellow at Harvard, City University of London, Hertie School, and Yonsei University. Led teams developing widely-used open source data science and data engineering tools. Author of \emph{Reproducible Research with R and RStudio} (Chapman \& Hall/CRC Press, 3rd Edition 2020)---a standard reference for research software development.

\vspace{0.25cm}
\medskip\hrule height 1pt
\vspace{0.5cm}

%%%%%%% Education %%%%%%%%%%%%%%
\section*{Education}

\noindent \textbf{London School of Economics}: PhD in Political Science, Quantitative Research Methodology (2008-2012). MRes with Distinction. MSc in Comparative Politics (2005-2006), Distinction. \\
\textbf{McGill University}: BA Honours in Political Science \& Geography (2003-2005), First Class Honours.

%%%%%%%  Other Skills %%%%%%%%%%%%%%
\section*{Other Skills}

\subsection*{Programming and Machine Learning}

I am proficient in AWS, Bash, BigQuery, CSS, GCP, Git/GitHub, HTML, JavaScript, Julia, Jupyter, LaTeX, Linux, SQL, Python, Pytorch, R, Shiny web apps, Stan, and Stata.

\end{document}
